### 2024-01-16 appendices/app_case_study.tex
Drop publications, first part of methodo + app. Pathway choice

\begin{table}[htbp!]
\caption{Major technologies used to supply the 2020-demands of \Cref{fig:cs_demands} in terms of share of production and installed capacity. $^{(a)}$ The decentralised heating units provide 98\% of the low-temperature heat demand. $^{(b)}$ The private mobility accounts for 80\% of the passengers mobility.}
\label{tab:Belgium_2020}
\begin{minipage}{\linewidth}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{l c c c}
\toprule
\multirow{2}{*}{\textbf{End-use demand}} & \textbf{Major} & \textbf{Share of} & \textbf{Installed}\\
    &	 \textbf{technologies} 	& \textbf{supply} & \textbf{capacity}	 \\ 	
\midrule							
\multirow{3}{*}{Electricity}
 & Nuclear & 39\% & 5.9\,GW\\
 & CCGT & 21\% & 3.9\,GW\\
 & Wind turbines & 14\% & 5.0\,GW\\
\midrule
\multirow{3}{*}{Heat High-Temp.}
 & Gas boiler & 36\% & 3.3\,GW\\
 & Coal boiler & 30\% & 2.3\,GW\\
 & Oil boiler & 20\% & 1.5\,GW\\
\midrule
\multirow{3}{*}{Heat Low-Temp. (DEC)$^{(a)}$}
 & Oil boiler & 48\% & 21.4\,GW\\
 & Gas boiler & 40\% & 17.5\,GW\\
 & Wood boiler & 10\% & 4.4\,GW\\
\midrule
\multirow{3}{*}{Heat Low-Temp. (DHN)}
 & Gas CHP & 59\% & 0.3\,GW\\
 & Gas boiler & 15\% & 0.3\,GW\\
 & Waste CHP & 15\% & 0.1\,GW\\
\midrule
\multirow{2}{*}{Private mobility$^{(b)}$}
 & Diesel car & 49\% & 93.5\,Mpass.-km/h\\
 & Gasoline car & 49\% & 94.7\,Mpass.-km/h\\
 & HEV & 2\% & 5.9\,Mpass.-km/h\\
\midrule
\multirow{3}{*}{Public mobility}
 & Diesel bus & 43\% & 3.6\,Mpass.-km/h\\
 & Train & 43\% & 3.9\,Mpass.-km/h\\
 & CNG bus & 5\% & 0.8\,Mpass.-km/h\\
\midrule
\multirow{3}{*}{Freight mobility}
 & Diesel truck & 74\% & 62.7\,Mt.-km/h\\
 & Diesel boat & 15\% & 10.8\,Mt.-km/h\\
 & Train & 11\% & 2.5\,Mt.-km/h\\
\midrule
HVC & Naphtha/LPG cracking & 100\% & 4.6\,GW\\
Ammonia & Haber-Bosch & 100\% & 1\,GW\\
Methanol & Import & 100\% & -\\
\bottomrule							
\end{tabular}}
\end{minipage}
\end{table}

@@

\begin{table}[htbp!]
\caption{Application of the uncertainty characterization method to the EnergyScope Pathway model for the year 2025. $^{(a)}$ Per \cite{Moret2017PhDThesis}, \og I: investment-type, II: operation-type (constant uncertainty over time), III: operation-type (uncertainty increasing over time)\fg. $^{(b)}$ The nominal values of each of the parameters is 0, meaning no variation compared to the nominal values of the impacted parameter in the model. $^{(c)}$ This range has been inferred from the local sensitivity analysis performed by \citet{PATHS2050}.}
\label{tab:UC_full}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{l l l c c c}
\toprule
\multirow{2}{*}{\textbf{Category}} & \multirow{2}{*}{\textbf{Parameter}} & \multirow{2}{*}{\textbf{Meaning}} & \multirow{2}{*}{\textbf{Type}$^{(a)}$}  & \multicolumn{2}{c}{\textbf{Relative variation$^{(b)}$}}\\
    & & & &	 min 	&	 max \\ 	
\midrule		
\multirow{4}{*}{\textbf{Cost of purchasing}} & $c_{\mathrm{op,fossil}}$ & Purchase fossil fuels & II & -64.3\% & 179.8\% \\
& $c_{\mathrm{op,elec}}$ & Purchase electricity & II & -64.3\% & 179.8\% \\
& $\bm{c_{\mathrm{op,electrofuels}}}$ & \textbf{Purchase electrofuels} & \textbf{II} & \textbf{-64.3\%} & \textbf{179.8\%} \\
& $c_{\mathrm{op,biofuels}}$ & Purchase biofuels & II & -64.3\% & 179.8\% \\
\midrule
\multirow{9}{*}{\textbf{Investment cost}} &$c_{\mathrm{inv,car}}$ & CAPEX car  & I & -21.6\% & 25.0\% \\
& $c_{\mathrm{inv,bus}}$ & CAPEX bus & I & -21.6\% & 25.0\% \\
& $c_{\mathrm{inv,ic\_prop}}$ & CAPEX ICE & I & -21.6\% & 25.0\% \\
& $c_{\mathrm{inv,e\_prop}}$ & CAPEX electric motor & I & -39.6\% & 39.6\% \\
& $c_{\mathrm{inv,fc\_prop}}$ & CAPEX fuel cell engine & I & -39.6\% & 39.6\% \\
& $c_{\mathrm{inv,efficiency}}$ & CAPEX efficiency measures & I & -39.3\%  & 39.3\% \\
& $c_{\mathrm{inv,PV}}$ & CAPEX PV & I & -39.6\% & 39.6\% \\
& $c_{\mathrm{inv,grid}}$ & CAPEX power grid & I & -39.3\% & 39.3\% \\
& $c_{\mathrm{inv,grid\_enforce}}$ & CAPEX grid reinforcement & I & -39.3\% & 39.3\% \\
& $\bm{c_{\mathrm{inv,nuclear\_SMR}}}$ & \textbf{CAPEX \gls{SMR}}$^{(c)}$ & \textbf{I} & \textbf{-40.0\%} & \textbf{44.0\%} \\
\midrule
\textbf{Maintenance cost} & $c_{\mathrm{maint,var}}$ & Variable OPEX of technologies & I & -48.2\% & 35.7\% \\
\midrule
\multirow{2}{*}{\textbf{Consumption}} &$\eta_{\mathrm{e\_prop}}$ & Consumption electric vehicles & I & -28.7\% & 28.7\% \\
& $\eta_{\mathrm{fc\_prop}}$ & Consumption fuel cell vehicles & I & -28.7\% & 28.7\% \\
\midrule
\multirow{3}{*}{\textbf{Potential installed capacity}} &$f_{\mathrm{max,PV}}$ & Max capacity PV & I & -24.1\% & 24.1\% \\
& $f_{\mathrm{max,windon}}$ & Max capacity onshore wind & I & -24.1\% & 24.1\% \\
& $f_{\mathrm{max,windoff}}$ & Max capacity offshore wind & I & -24.1\% & 24.1\% \\
\midrule
\multirow{2}{*}{\textbf{Hourly load factor}} & $c_{\mathrm{p,t,PV}}$ & Hourly load factor PV & II & -22.1\% & 22.1\% \\
& $c_{\mathrm{p,t,winds}}$ & Hourly load factor wind turbines & II & -22.1\% & 22.1\% \\
\midrule
\multirow{2}{*}{\textbf{Resource availability}} & $avail_{\mathrm{elec}}$ & Available electricity import & I & -32.1\% & 32.1\% \\
& $avail_{\mathrm{biomass}}$ & Available local biomass & I & -32.1\% & 32.1\% \\
\midrule

@@

\end{tabular}}
\end{table}

>>>>

\begin{table}[htbp!]
\caption{Major technologies used to supply the 2020-demands of \Cref{fig:cs_demands} in terms of share of production and installed capacity.}
\label{tab:Belgium_2020}
\begin{minipage}{\linewidth}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{l c c c}
\toprule
\multirow{2}{*}{\textbf{End-use demand}} & \textbf{Major} & \textbf{Share of} & \textbf{Installed}\\
    &	 \textbf{technologies} 	& \textbf{supply} & \textbf{capacity}	 \\ 	
\midrule							
\multirow{3}{*}{Electricity}
 & Nuclear & 39\% & 5.9\,GW\\
 & CCGT & 21\% & 3.9\,GW\\
 & Wind turbines & 14\% & 5.0\,GW\\
\midrule
\multirow{3}{*}{Heat High-Temp.}
 & Gas boiler & 36\% & 3.3\,GW\\
 & Coal boiler & 30\% & 2.3\,GW\\
 & Oil boiler & 20\% & 1.5\,GW\\
\midrule
\multirow{3}{*}{Heat Low-Temp. (DEC)\footnote{\label{foot:DHN_98}The decentralised heating units provide 98\% of the low-temperature heat demand. }}
 & Oil boiler & 48\% & 21.4\,GW\\
 & Gas boiler & 40\% & 17.5\,GW\\
 & Wood boiler & 10\% & 4.4\,GW\\
\midrule
\multirow{3}{*}{Heat Low-Temp. (DHN)}
 & Gas CHP & 59\% & 0.3\,GW\\
 & Gas boiler & 15\% & 0.3\,GW\\
 & Waste CHP & 15\% & 0.1\,GW\\
\midrule
\multirow{2}{*}{Private mobility\footnote{\label{foot:privatemob_80}The private mobility accounts for 80\% of the passengers mobility.}}
 & Diesel car & 49\% & 93.5\,Mpass.-km/h\\
 & Gasoline car & 49\% & 94.7\,Mpass.-km/h\\
 & HEV & 2\% & 5.9\,Mpass.-km/h\\
\midrule
\multirow{3}{*}{Public mobility}
 & Diesel bus & 43\% & 3.6\,Mpass.-km/h\\
 & Train & 43\% & 3.9\,Mpass.-km/h\\
 & CNG bus & 5\% & 0.8\,Mpass.-km/h\\
\midrule
\multirow{3}{*}{Freight mobility}
 & Diesel truck & 74\% & 62.7\,Mt.-km/h\\
 & Diesel boat & 15\% & 10.8\,Mt.-km/h\\
 & Train & 11\% & 2.5\,Mt.-km/h\\
\midrule
HVC & Naphtha/LPG cracking & 100\% & 4.6\,GW\\
Ammonia & Haber-Bosch & 100\% & 1\,GW\\
Methanol & Import & 100\% & -\\
\bottomrule							
\end{tabular}}
\end{minipage}
\end{table}

@@

%$^{(a)}$ Per \cite{Moret2017PhDThesis}, \og I: investment-type, II: operation-type (constant uncertainty over time), III: operation-type (uncertainty increasing over time)\fg. $^{(b)}$ The nominal values of each of the parameters is 0, meaning no variation compared to the nominal values of the impacted parameter in the model. $^{(c)}$ This range has been inferred from the local sensitivity analysis performed by \citet{PATHS2050}.

\begin{table}[htbp!]
\caption{Application of the uncertainty characterization method to the EnergyScope Pathway model for the year 2025. }
\label{tab:UC_full}
\begin{minipage}{\linewidth}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{l l l c c c}
\toprule
\multirow{2}{*}{\textbf{Category}} & \multirow{2}{*}{\textbf{Parameter}} & \multirow{2}{*}{\textbf{Meaning}} & \multirow{2}{*}{\textbf{Type}\footnote{\label{foot:type_uncert_range}Per \cite{Moret2017PhDThesis}, \og I: investment-type, II: operation-type (constant uncertainty over time), III: operation-type (uncertainty increasing over time)\fg . }}  & \multicolumn{2}{c}{\textbf{Relative variation}\footnote{\label{foot:nom_val_uncert}The nominal values of each of the parameters is 0, meaning no variation compared to the nominal values of the impacted parameter in the model. }}\\
    & & & &	 min 	&	 max \\ 	
\midrule		
\multirow{4}{*}{\textbf{Cost of purchasing}} & $c_{\mathrm{op,fossil}}$ & Purchase fossil fuels & II & -64.3\% & 179.8\% \\
& $c_{\mathrm{op,elec}}$ & Purchase electricity & II & -64.3\% & 179.8\% \\
& $\bm{c_{\mathrm{op,electrofuels}}}$ & \textbf{Purchase electrofuels} & \textbf{II} & \textbf{-64.3\%} & \textbf{179.8\%} \\
& $c_{\mathrm{op,biofuels}}$ & Purchase biofuels & II & -64.3\% & 179.8\% \\
\midrule
\multirow{9}{*}{\textbf{Investment cost}} &$c_{\mathrm{inv,car}}$ & CAPEX car  & I & -21.6\% & 25.0\% \\
& $c_{\mathrm{inv,bus}}$ & CAPEX bus & I & -21.6\% & 25.0\% \\
& $c_{\mathrm{inv,ic\_prop}}$ & CAPEX ICE & I & -21.6\% & 25.0\% \\
& $c_{\mathrm{inv,e\_prop}}$ & CAPEX electric motor & I & -39.6\% & 39.6\% \\
& $c_{\mathrm{inv,fc\_prop}}$ & CAPEX fuel cell engine & I & -39.6\% & 39.6\% \\
& $c_{\mathrm{inv,efficiency}}$ & CAPEX efficiency measures & I & -39.3\%  & 39.3\% \\
& $c_{\mathrm{inv,PV}}$ & CAPEX PV & I & -39.6\% & 39.6\% \\
& $c_{\mathrm{inv,grid}}$ & CAPEX power grid & I & -39.3\% & 39.3\% \\
& $c_{\mathrm{inv,grid\_enforce}}$ & CAPEX grid reinforcement & I & -39.3\% & 39.3\% \\
& $\bm{c_{\mathrm{inv,nuclear\_SMR}}}$ & \textbf{CAPEX \gls{SMR}}\footnote{\label{foot:range_SMR}This range has been inferred from the local sensitivity analysis performed by \citet{PATHS2050}.} & \textbf{I} & \textbf{-40.0\%} & \textbf{44.0\%} \\
\midrule
\textbf{Maintenance cost} & $c_{\mathrm{maint,var}}$ & Variable OPEX of technologies & I & -48.2\% & 35.7\% \\
\midrule
\multirow{2}{*}{\textbf{Consumption}} &$\eta_{\mathrm{e\_prop}}$ & Consumption electric vehicles & I & -28.7\% & 28.7\% \\
& $\eta_{\mathrm{fc\_prop}}$ & Consumption fuel cell vehicles & I & -28.7\% & 28.7\% \\
\midrule
\multirow{3}{*}{\textbf{Potential installed capacity}} &$f_{\mathrm{max,PV}}$ & Max capacity PV & I & -24.1\% & 24.1\% \\
& $f_{\mathrm{max,windon}}$ & Max capacity onshore wind & I & -24.1\% & 24.1\% \\
& $f_{\mathrm{max,windoff}}$ & Max capacity offshore wind & I & -24.1\% & 24.1\% \\
\midrule
\multirow{2}{*}{\textbf{Hourly load factor}} & $c_{\mathrm{p,t,PV}}$ & Hourly load factor PV & II & -22.1\% & 22.1\% \\
& $c_{\mathrm{p,t,winds}}$ & Hourly load factor wind turbines & II & -22.1\% & 22.1\% \\
\midrule
\multirow{2}{*}{\textbf{Resource availability}} & $avail_{\mathrm{elec}}$ & Available electricity import & I & -32.1\% & 32.1\% \\
& $avail_{\mathrm{biomass}}$ & Available local biomass & I & -32.1\% & 32.1\% \\
\midrule

@@

\end{tabular}}
\end{minipage}
\end{table}
